\documentclass[11pt,a4paper,twoside,onecolumn,openany,final,oldfontcommands]{memoir}
\usepackage{sty/FOBOS}  % FOBOS SDN style file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Things you need to edit:
%   - Document name, numbering, and date; edit the newcommands below.
%   - Authors list; see authors.tex
%   - The contact information for the corresponding author; see corresponding.tex
%   - Any (additional) tex aliases you would like to include; see aliases.tex
%   - BibTex references are included using ref.bib
%   - Main body of the document
%   - Add a line to the revision history

\newcommand{\doclongname}{FIDDLES Prototyping Report}
\newcommand{\docshortname}{FIDDLES}

\newcommand{\project}{FOBOS}
\newcommand{\wbs}{FBR}
\newcommand{\doctype}{DOC}
\newcommand{\docnumber}{001}

% Pre-release versions are 0A - ZZ; Release versions should be 01-99
\newcommand{\docversion}{0A}
\newcommand{\docreleaseDate}{2020-07-15}  % Please use ISO-8601 YYYY-MM-DD format.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Document Designation Number
\newcommand{\docsysnum}{{\project}.{\wbs}.{\doctype}.{\docnumber}.V{\docversion}}

%% Set footers to use document info
%% ================================
\makeoddfoot{Ruled}{\docsysnum}{}{\thepage\ / \thelastpage}
\makeevenfoot{Ruled}{\thepage\ / \thelastpage}{}{\docsysnum}

%%% Packages for TESTING
\usepackage{lipsum}
\listfiles

%% ALIASES
\input{aliases}

%%%% BEGIN DOCUMENT
\begin{document}
\bibliographystyle{sty/aasjournal}

%%% FRONTMATTER
\frontmatter
\input{title}
\thispagestyle{empty}  % Title page has no page number shown.

\clearpage
\setupmaintoc
\tableofcontents 

\clearpage
\listoffigures

%: PREFACE
\chapter{Corresponding Author}
%
\input{corresponding}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The rest of the document editing begins here

%-----------------------------------------------------------------------
% Executive Summary
\chapter{Executive Summary}

This is the template for FOBOS design documents.

%-----------------------------------------------------------------------


%-----------------------------------------------------------------------
% Main document body
\mainmatter

% Introduction
\chapter{Introduction}

Here is a reference: \citet{2019BAAS...51g.198B}.

% Chapter
\chapter{Examples}

Because many of the documents are versioned using git, we need to adopt some practices that ease/enable the git merging.  Generally, try to keep paragraphs on a single line, like this one.  Also try to keep other text-editor-specific changes to the format of the text to a minimum (e.g., keep items in a list on a single line, figure captions, table captions, etc).  Regardless, when editing off Overleaf, make sure that you check the merging from/to the main repository to ensure your edits are correctly integrated.

The main document style is set to {\ttfamily memoir}, which has a few
modifications for lists.  Two examples are shown below.  Particularly
note the use of the comment character and how this affects the spacing
between the list and the adjoining paragraph.

\tightlists
\begin{enumerate}
%
\item Enumerated item in {\ttfamily memoir}, with
%
\item tight lists.
%
\end{enumerate}
%
Please also consider using {\ttfamily paralist} (already in package listing above).  The following {\ttfamily paralist} enumerated environments are useful:
\begin{inparaenum}[(a)]
%
\item asparaenum
%
\item inparaenum, and
%
\item compactenum.
%
\end{inparaenum}
%
The itemized versions are also useful:
%
\begin{asparaitem}
%
\item asparaitem
%
\item inparaitem
%
\item compactitem
%
\end{asparaitem}
%
Note that the fonts for the equations are different than the text.  These font changes are handled in the {\ttfamily FOBOS.sty} file.  Here is an inline equation --- $E=mc^2$ --- and here is the same one but isolated and numbered:
%
\begin{equation}
E = m c^2
\end{equation}

\section{Section}

Here is a section of this chapter.  Note how it is enumerated here and in the table of contents.

\subsection{Sub-section}

Subsections also appear in the table of contents.

\paragraph{Test}

There is no {\ttfamily subsubsection}; use {\ttfamily paragraph} instead (if necessary).  The paragraphs just have bold text that provides the paragraph title and then the rest of the paragraph is normal, including the indentation.

\newpage

%% Chapter
\chapter*{Revision History}
\addcontentsline{toc}{chapter}{Revision History}

\begin{table}[hp]{%
\begin{tabular}{l | l | l |  p{22pc}} \toprule
{\bf Version} & {\bf Date} & {\bf Editor} & {\bf Comments} \\ \midrule
% Insert your own version number with the date, your name, and a short
% description of this version of the document.
0A & 2020-07-08 & Kyle Westfall & Initial version \\ \bottomrule
\end{tabular}}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{ref}

\end{document}


